\documentclass[twocolumn]{zett}
\input{preambles}
\title{grass is always greener on the other side}
\author{Frank Tsai}
\date{\today}
%\thanks{}
\begin{document}

\begin{node}
  \textbf{Vision vs. processing}.
  Descriptions of images vs. new images.
\end{node}

\begin{node}
  \textbf{Image formation factors}.
  Lighting conditions, scene geometry, surface properties, and camera properties.
\end{node}

\begin{node}
  \textbf{Physical parameters of image formation}.
  Optics, sensor, geometry, photometry.
\end{node}

\begin{node}
  The \textbf{depth of field} is the distance between image planes where blur is tolerable.
\end{node}

\begin{node}
  Smaller aperture increases the range in which the object is approximately in focus.
\end{node}

\begin{node}
  \textbf{f-number}.
  Greater f-number = darker images.
  Brightness (illuminance) $\sim$ brightness of scene in len's FoV (luminance).
  Decreases $\sim$ square of f-number.
\end{node}

\begin{node}
  \textbf{CCD (charged-coupled device)}.
  Most common, high sensitivity, high power, can't be individually addressed, blooming.
\end{node}

\begin{node}
  \textbf{CMOS}.
  Cheap to fab, low sensitivity, low power, can be individually addressed.
\end{node}

\begin{node}
  \textbf{Bayer pattern}.
  More green because human vision is more sensitive to green.
  50\% green, 25\% red, 25\% blue.
\end{node}

\begin{node}
  \textbf{Light flux}.
  Power emitted within a solid angle.
\end{node}

\begin{node}
  \textbf{Radiant intensity}.
  Light flux emitted per unit solid angle.
\end{node}

\begin{node}
  \textbf{Surface irradiance}.
  Light flux incident per unit surface area.
\end{node}

\begin{node}
  \textbf{Surface radiance}.
  Light flux emitted per unit foreshortened area per unit solid angle.
\end{node}

\begin{node}
  Image irradiance is proportional to scene radiance.
\end{node}

\begin{node}
  Image brightness does not vary with scene depth.
\end{node}

\begin{node}
  \textbf{Reflection mechanisms}.
  Image intensity = surface (mirror, glass) + body (diffuse, matte, clay, paper).
\end{node}

\begin{node}
  Color = convex combination of color of body reflection and color of surface reflection.
\end{node}

\begin{node}
  \textbf{Image multiplication}.
  Masking.
\end{node}

\begin{node}
  \textbf{Image division}.
  Shading correction.
\end{node}

\begin{node}
  \textbf{Binary image}.
  Zeroth moment = area.
  First moment = center of area.
  Least second moment = orientation (orthogonal to max second moment).
\end{node}

\begin{node}
  Roundedness = min second / max second.
\end{node}

\begin{node}
  \textbf{2x2 matrix transformation}.
  Origin $\to$ origin.
  Line $\to$ line.
  Parallel $\to$ parallel.
  Closed under comp.
\end{node}

\begin{node}
  \textbf{Affine transformation}.
  Origin $\not\to$ origin.
  Line $\to$ line.
  Parallel $\to$ parallel.
  Closed under comp.
\end{node}

\begin{node}
  \textbf{Homographic transformation}.
  Origin $\not\to$ origin.
  Line $\to$ line.
  Parallel $\not\to$ parallel.
  Closed under comp.
\end{node}

\begin{node}
  \begin{tabular}{cccc}
    name & matrix & 2D DoF & 3D DoF\\\hline
    translation & $[I | t]$ & 2 & 3\\\hline
    rigid & $[R | t]$ & 3 & 6\\\hline
    similarity & $[sR | t]$ & 4 & 7\\\hline
    affine & $[A]$ & 6 & 12\\\hline
    homography & $[H]$ & 8 & 15\\\hline
  \end{tabular}
\end{node}

\begin{node}
  \textbf{Salt and pepper noise}.
  Random black and white.
\end{node}

\begin{node}
  \textbf{Impulse noise}.
  Random white.
\end{node}

\begin{node}
  \textbf{Gaussian noise}.
  Variation in intensity drawn from GND.
\end{node}

\begin{node}
  \textbf{LSIS}.
  Linear shift invariant system.
\end{node}

\begin{node}
  \textbf{Median filtering}.
  Good for simple noise.
  Not good for not simple noise.
\end{node}

\begin{node}
  Fourier transform useful because easier to remove unwanted frequencies and faster to compute some operations.
\end{node}

\begin{node}
  \textbf{Phase} preserves geometric information.
  Modulus does not.
\end{node}

\begin{node}
  \textbf{Weiner deconvolution} compensates amplified high-frequency noise.
\end{node}

\begin{node}
  \textbf{RGB} - screen, camera.
  \textbf{CMYK} - printers.
  \textbf{HSI} - human describable model.
  \textbf{CIE Lab} - device independent model.
\end{node}

\begin{node}
  \textbf{Edge} - rapid change in image intensity within a small region.
  \textbf{Corner} - rapid change in all directions.
\end{node}

\begin{node}
  $f$ is an image.
  $\frac{df}{dx}$ - local extrema = edges.
  $\frac{d^{2}f}{dx^{2}}$ aka Laplacian - local maxima = edges.
  $\nabla f$ - image gradient = direction of most rapid increase in intensity.
  \textbf{Finite difference approx} of $\nabla f$ is a convolution.
\end{node}

\begin{node}
  \textbf{Hysteresis edge threshold}.
  Two thresholds $t_{0}$, $t_{1}$.
  $\lVert \nabla f \rVert < t_{0}$ - def not an edge.
  $\lVert \nabla f \rVert > t_{1}$ - def an edge.
  $t_{0} \leq \lVert \nabla f \rVert < t_{1}$ - an edge if a neighbor is def an edge.
\end{node}

\begin{node}
  \begin{tabular}{cc}
    Gradient & Laplacian\\\hline
    location, modulus, direction & only location\\\hline
    Maxima threshold detection & zero-crossing detection\\\hline
    non-linear, needs 2 conv & linear, needs 1 conv
  \end{tabular}
\end{node}

\begin{node}
  \textbf{Harris corner detection}.
  Both eigenvalues small - flat.
  Both eigenvalues similar - corner.
  One eigenvalue much larger - edge.
\end{node}

\begin{node}
  \textbf{Canny edge detector}.
  Filter image with derivative of Gaussian $\to$ find magnitude and orientation of gradient $\to$ non maximum supression: thin multi pixel ridges down to single pixel $\to$ linking and threshold (hysteresis) use high threshold to start edge curve and low threshold to continue them (wtf does it even mean??)
\end{node}

\begin{node}
  \textbf{Hough transform}.
  Points in image space become lines in parameter space.
  Circles in image space become cones in parameter space.
  Works on disconnected edges.
  Relatively insensitive to occlusion and noise.
  Effective for simple shapes.
  Complex shapes: generalized Hough transform.
  Trade-off between work in image space and parameter space.
  Robust to outliers: each point votes separately.
\end{node}

\begin{node}
  \textbf{Contour}.
  An ordered list of control points connected by line segments of fixed length.
  Goal is to maximize sum of gradient magnitude squared.
\end{node}

\begin{node}
  \textbf{Object detection}.
  Invariant descriptors: translation, rotation, scaling, illumination, occlusion.
  Impacted by noise, blur, compression artifacts.
  Local features: intensity - not a good choice, edge - poor localization, corner - ok for simple objects.
  Global features: area, roundedness - useful for binary images, histogram - not invariant to intensity.
\end{node}

\begin{node}
  \textbf{SIFT}.
  Principal orientation - maximum in the histogram.
  Robust to clutter.
  Descriptors - compute gradient orientation normalized histogram of each of the four quadrants.
\end{node}

\begin{node}
  \textbf{RANSAC}.
  Choose $s$ samples (usually minimum needed to fit model) randomly.
  Count number of inliers.
  Repeat for some times.
  Choose the best model.
  For homography, $s = 4$.
\end{node}

\begin{node}
  \textbf{Forward warping} - can result in holes.
  \textbf{Backward warping} - fixes this.
\end{node}

\begin{node}
  \textbf{Bakic flesh finder}.
  Convert image to normalized space.
  Use a classifier to find skin.
  Find large connected components.
\end{node}

\begin{node}
  \textbf{Haar features}.
  Intensity in white $-$ intensity in black.
\end{node}

\begin{node}
  \textbf{Integral image}.
  This is just dynamic programming...
\end{node}

\begin{node}
  \textbf{Nearest neighbor classifier}.
  Larger training set = more robust NNC.
  SVM - maximizes margin of decision boundary.
\end{node}

\begin{node}
  \textbf{Boosting} for feature selection.
  Train weak classifiers, increase weight where mistakes made, train another weak classifier, combine them.
  Good vs SVM: integrates training and feature selection, training is linear not quadratic, flexibility in choice of weak learners, boosting scheme, testing is fast.
  Bad vs SVM: need many examples, slow training, does not work as well as SVM (esp many-class).
\end{node}

\begin{node}
  \textbf{Attentional cascade} chain increasingly more complex classifiers.
  Reject non-face early.
\end{node}

\begin{node}
  \textbf{Training cascade}.
  Set target detection and false pos rates for each stage.
  Keep adding features until targets met.
  If false pos rate not low enough, add stage.
  Use false pos from current stage as training examples for next.
\end{node}

\begin{node}
  Face detection systems mature not perfect.
  Frontal and side need different face models.
\end{node}

\begin{node}
  Baseline - distance between camera.
  Disparity - distance between pixels of some point on surface.
  Depth $z$ is inversely proportional to disparity.
  Disparity is proportional to baseline.
\end{node}

\begin{node}
  \textbf{Window-based matching problems}: surface can't be repetitive.
  Foreshortening effect.
  Small window = sensitive to noise.
  Large window = poor localization.
  Adaptive window - use multiple sizes and use the best one.
\end{node}

\begin{node}
  \textbf{Uncalibrated stereo}.
  Intrinsics of cameras known.
  Extrinsics unknown.
\end{node}

\begin{node}
  \textbf{Epipole} - coordinate of one camera's origin in the other camera's image plane.
  Every scene point lies on a unique epipolar plane.
  Find epipolar line.
  Use triangulation to compute depth.
\end{node}

\begin{node}
  \textbf{Optical flow}.
  Ideally, optical flow = motion field.
  Not always the case: barber pole illusion, stationary sphere, spinning sphere.
\end{node}

\begin{node}
  We can't determine optical flow parallel to the constraint line.
\end{node}

\begin{node}
  \textbf{Lucas-Kanade solution}.
  Assumes motion field and optical flow is constant within a small neighborhood.
  $A^{T}A$ must be invertible and well-conditioned: their eigenvalues are not too small (smooth region) and not too different (edge).
  Coarse-to-fine estimation.
\end{node}

\end{document}
